---
title: "DATA607_Assignment9"
author: "IvanTikhonov"
date: "2022-10-27"
output: html_document
---
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and
transform it into an R DataFrame.

Libraries
```{r}
# Loading the necessary libraries
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggplot2)
library(dbplyr)
library(jsonlite)
library(httr)
library(DT)
library(kableExtra)
```

Connect to the API
I will be using the movies API, filtered for the following sections:
Let’s first read in the data from the API:

```{r}
url <- "https://api.nytimes.com/svc/movies/v2/reviews/search.json"
api.key <- "vx4VGIrlkceM9FlIZZU35sADhGfXAmK7"
url <- paste0(url, '?api-key=', api.key)
df <- fromJSON(url, flatten = TRUE)
datatable(df$results)
```





